### 2025-03-01 report/CONJ_FRANCE.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_COMD.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_FRANCE.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/CONJ_INDUSTRIE.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_FRANCE.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_INDUSTRIE.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/CONJ_SERV.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_INDUSTRIE.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_SERV.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/CONSO.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONJ_SERV.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONSO.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/CREATION_ENT.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/CONSO.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ENT.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/ICAM.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ENT.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ICAM.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/ICA_ind.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ICAM.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ICA_ind.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/IPI.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/ICA_ind.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/IPI.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

### 2025-03-01 report/IVV.qmd
template creation

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/IPI.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---

>>>>

---
format: 
  html:
    toc: true
    number-sections: true
    embed-ressources: true
    number-depth: 2
date: today
date-format: long
params:
  file: "../data/IVV.yml"
execute:
  cache: true
author:
  - name: Alain Quartier-la-Tente 
    affiliation: LEMNA
    orcid: 0000-0001-7890-3857
comments: 
    hypothesis:
      theme: clean
echo: false
eval: true
---
